% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd or http://www.gratisoft.us/todd/resume.html
% (c) 2009 Jason Antman <jason@jasonantman.com> http://www.jasonantman.com
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Jason Antman}  & 201.906.7347\\
2023 Loch Haven Dr. SE&
\href{mailto:jason@jasonantman.com}{jason@jasonantman.com} \\
Conyers, GA 30013&
\href{http://resume.jasonantman.com}{resume.jasonantman.com} \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Work Experience}
\begin{itemize}
\item
  \ressubheading{Cox Automotive / Manheim}{Atlanta, GA}{Sr. Software Developer - Release Engineering Tooling}{September 2015 - Present}
	\begin{itemize}
								\resitem{Evangelized code review, unit testing and CI/CD for Release Engineering's own tooling. Presented and evangelized RE products to management and software development teams.}
                \resitem{Architecture, design, deployment and support lead for Hashicorp Vault implementation including functional and security monitoring, extensive related tooling, automated deployment, documentation, DR procedures, and application integration.}
								\resitem{Backup and disaster recovery tooling and procedures for widely-used production Consul cluster.}
								\resitem{Extensive development for our in-house self-service Jenkins infrastructure project; automated unit and acceptance tests, swarm node management, Vault integration, documentation, release/versioning/upgrade process.}
								\resitem{Implemented self-service administrative tool for globally searching GitHub Enterprise.}
								\resitem{Docker Distribution (Registry v2) implementation, automation, upgrade and disaster recovery.}
								\resitem{Lead internal implementation of Capital One's Cloud Custodian; extensive policy development, supporting tooling and monitoring.}
								\resitem{Expanded and evangelized use of AWS Lambda for administrative and internal tasks.}
	\end{itemize}
\item
	\ressubheading{Cox Media Group - Digital (CMGd)}{Atlanta, GA}{Automation \& Tools Engineer}{June 2013 - September 2015}
	\begin{itemize}
                \resitem{Designed and developed large portions of ``batteries-included'' (CloudWatch, NewRelic, Logstash) single-click Python webapp deployment tooling using Puppet, Packer and AWS CloudFormation (Troposphere and Boto). Replicated for Wordpress and ported to internal VMWare environment.}
                \resitem{Developed and implemented AWS tagging standard for complete per-app cost tracking (using NetFlix Ice); implemented AWS cost saving measures to reduce cost of some applications by up to 60\%.}
                \resitem{Designed Puppet3 infrastructure using latest best practices; planned and executed migration of ~300 existing nodes to new infrastructure, including monitoring and deployment / testing / promotion of code.}
                \resitem{Took lead role in design/planning and build-out of multiple production-like test environments. Cut build-out time for subsequent environments by approximately 75\%.}
	\end{itemize}

\item
	\ressubheading{Cox Media Group - Digital (CMGd)}{Atlanta, GA}{Systems Engineer}{October 2012 - June 2013}
	\begin{itemize}
                \resitem{General and On-Call duties in a large (10.5M views/day) and fast-paced Django web environment.}
                \resitem{Designed and deployed multi-node Graphite cluster for metric storage and display; began alerting off of metrics.}
                \resitem{Proof of concept for migration from Nagios with NagioSQL configuration to Icinga with Puppet-generated configuration.}
                \resitem{Rewrote Puppet yum/rpm version comparison to fix numerous bugs; merged and released in puppet4.}
	\end{itemize}

\item
	\ressubheading{TechTarget  (NASDAQ: TTGT)}{Alpharetta, GA}{System Administrator}{November 2011 - October 2012}
	\begin{itemize}
		            \resitem{Design and implementation of Puppet-based configuration management and provisioning for all new server deployments.}
                \resitem{Technical lead - monitoring and performance analysis of Linux OS, application software, and VMWare; development of internal tools and infrastructure; lead/architect for Nagios, collectd, centralized logging, log analysis, and DNS infrastructure redesign.}
	\end{itemize}
\item
	\ressubheading{Rutgers University - Central Systems \& Services}{Piscataway, NJ}{System Administrator}{September 2007 - October 2011}
	\begin{itemize}
                \resitem{Specification, design, implementation and ongoing second-level support of centralized production services including configuration management (Puppet), DHCP, WPA2/RADIUS authentication and accounting, centralized logging (rsyslog), residential (dorm) network authentication / registration / DHCP infrastructure (30,000+ users).}
                \resitem{Investigated security issues on campus wireless network; identified and analyzed security vulnerabilities in vendor-supplied software and hardware.}
                \resitem{Third-level support and troubleshooting of campus-wide wireless network and wired residential network issues. Assisted with network administration tasks.}
		            \resitem{Development and proof-of-concept of University common area wired 802.1x authentication, with captive portal and MAC auth fall-through.}
		            \resitem{Development and support of custom Linux-based appliances / embedded network devices.}
	\end{itemize}

\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Rutgers University}{Piscataway, NJ}{BA, Information Technology and Informatics}{January 2006 - October 2009}
	\begin{itemize}
		\resitem{BA in Information Technology and Informatics, Rutgers
                College / School of Communication and Information. Minor in
                General History.}
	\end{itemize}
\end{itemize}

\resheading{Volunteer Experience}
\begin{itemize}
\item
        \ressubheading{Midland Park Ambulance Corps}{Midland Park, NJ}{(501(c)(3) non-profit)}{January 2006 - January 2012}
        \begin{itemize}
                \resitem{Responsible for engineering and administration of internal network, applications, and Internet-accessible resources supporting 911 Emergency Medical response as a local, county and state resource.}
                \resitem{Design, development and ongoing support of a custom application to manage patient care records, crew scheduling, internal administrative functions, finances/budgeting, and VoIP-based crew member response tracking.}
                \resitem{Served in numerous capacities including EMT-B, Crew Chief, By-Laws Committee Chairman, Computer Committee Chairman, Treasurer and First Lieutenant (operational second-in-command).}
        \end{itemize}
\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
Current languages: Python (six years), Ruby (three years). Basic or previous knowledge of Groovy, PHP, Perl, bash.
% using linux since 2002. Admin since 2007.
\item[Operating Systems:]
Twelve years experience in use and administration of Linux; ten years experience architecting and administering production Linux servers and applications.
Primarily CentOS/RedHat on servers and AWS, Arch Linux personally. Experience with Vyatta Network OS/VyOS, Cisco CatOS and IOS.
\item[Software:]
Many Amazon (AWS) offerings. Hashicorp Terraform, Vault, Consul, Packer, and related tools. Jenkins. Puppet. Graphite, Logstash/Elasticsearch, rsyslog, Nagios/Icinga. MySQL, PostgreSQL. Apache httpd, nginx. Git.
Former experience with Solr, Postfix, ISC BIND9, ISC dhcpd, FreeRADIUS, Asterisk, OpenLDAP.

\item[Platforms:]
AWS. Previous experience with many datacenter technologies: VMWare, most Enterprise-grade server hardware, F5 Big-IP Load Balancers, network hardware, embedded devices, Meru and BlueSocket wireless hardware. Previous experience in datacenter operations and physical infrastructure (copper/fiber/power) management.
\end{description}

\resheading{Open Source Projects and Contributions}
\begin{description}
\item{See \href{http://resume.jasonantman.com}{resume.jasonantman.com} for highlights or \href{https://github.com/jantman}{https://github.com/jantman}.}
\end{description}

\end{document}
