% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd or http://www.gratisoft.us/todd/resume.html
% (c) 2009 Jason Antman <jason@jasonantman.com> http://www.jasonantman.com
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Jason Antman}  & 201.906.7347\\
413 Renaissance Way&  jason@jasonantman.com \\
Conyers, GA 30012& resume.jasonantman.com - github.com/jantman\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Rutgers University}{Piscataway, NJ}{BA, Information Technology and Informatics}{January 2006 - October 2009}
	\begin{itemize}
		\resitem{BA in Information Technology and Informatics, Rutgers
                College / School of Communication and Information. Minor in
                General History.}
	\end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{CMG Digital}{Atlanta, GA}{Automation \& Tooling Engineer}{June 2013 - Present}
	\begin{itemize}
                \resitem{Designed Puppet3 infrastructure using latest best practices, planned and excuted migration of existing nodes to new infrastructure. This included monitoring, and deployment/testing/promotion of code.}
                \resitem{Took lead role in design/planning and buildout of multiple production\-like test environments; cut buildout time for environments 2+ by approximately 75\%.}
                \resitem{Automated development environment creation to reduce buildout time by 60\%.}
                \resitem{Deployed Selenium Grid for internal automated browser tests.}
                \resitem{Planned use of environment variables in Apache httpd configurations to replace divergent configuration with a single git repository promoted between environments.}
                \resitem{Assisted small team with overhaul of nightly production to dev environment database clone procedure (500GB PostgresQL database).}
                \resitem{Developed prod-like Vagrant-based local development environment for main application (Django CMS).}
                \resitem{Assisted in planning and development for single-click application stacks in AWS using Puppet, Packer and CloudFormation.}
                \resitem{Many contributions to Puppet and community modules.}
                \resitem{Developed vagrant-r10k plugin to allow provisioning puppet modules for Vagrant via r10k Puppetfile.}
	\end{itemize}

\item
	\ressubheading{CMG Digital}{Atlanta, GA}{Systems Engineer}{October 2012 - June 2013}
	\begin{itemize}
                \resitem{General and On-Call duties in a large and fast-paced web media environment.}
                \resitem{Assiested with ops side of major application settings refactor project.}
                \resitem{Deployed RPM build environment for internal and rebuilt external packages.}
                \resitem{Deployed 3-node Graphite cluster for metric storage and display; began alerting off of metrics.}
                \resitem{Packaged RPMs of Apache Tomcat and Zookeeper and NodeJS for internal deployment.}
                \resitem{Proof of concept for migration from Nagios/NagiosQL to Icinga with Puppet-generated configuration.}
	\end{itemize}

\item
	\ressubheading{TechTarget  (NASDAQ: TTGT)}{Alpharetta, GA}{System Administrator}{November 2011 - Present}
	\begin{itemize}
		\resitem{Design and implementation of Puppet-based configuration management and provisioning for all new server deployments.}
                \resitem{Technical lead - monitoring and performance analysis of Linux OS and application software, VMWare ESX/vCenter5/vSphere; distributed Nagios and collectd infrastructure, Veeam One virtualization monitoring for end-users, Tidal Enterprise Scheduler.}
                \resitem{Development of internal tools and infrastructure; technical lead/architect for centralized logging, log analysis, DNS infrastructure redesign.}
	\end{itemize}

\item
	\ressubheading{Rutgers University - Central Systems \&
          Services}{Piscataway, NJ}{System Administrator}{September 2007 - October 2011}
	\begin{itemize}
                \resitem{Specification, design, implementation and ongoing second-level support of centralized production services including configuration management (Puppet), DHCP, WPA2/RADIUS authentication and accounting, centralized logging (rsyslog), residential (dorm) network authentication/registration/DHCP infrastructure.}
                \resitem{Extensive scripting and custom tool development
                  (PHP/Ajax, some Java and Python)
                  - Linux services, Puppet, ISC dhcpd, FreeRADIUS, Meru and BlueSocket wireless equipment, etc.}
                \resitem{Investigated security issues on campus wireless network; identified and analyzed security vulnerabilities in vendor-supplied software.}
                \resitem{Third-level support and troubleshooting of campus-wide wireless network and wired residential network issues. Assisted with network administration tasks.}
                \resitem{Management of Nagios and Cacti for availability and performance monitoring.}
		\resitem{Development and proof-of-concept of University common area wired 802.1x authentication, with captive portal and MAC auth fall-through.}
		\resitem{Development of server configuration and security
                  policies, and compliance audit tools.}
	\end{itemize}

\item
        \ressubheading{Sun Microsystems}{Somerset, NJ}{Campus Ambassador}{September 2007 - June 2008}
        \begin{itemize}
                \resitem{Campus Ambassador to Rutgers University, responsible for spreading awareness of Sun's open-source product offerings (OpenSolaris, NetBeans, Java) among students, faculty, and staff.}
        \end{itemize}

\item
	\ressubheading{Rutgers University - NetOps}{Piscataway, NJ}{Student Systems Programmer}{April 2006 - May 2007}
	\begin{itemize}
		\resitem{Responsible for various web application programming projects, primarily developed for
                  PHP/MySQL on Linux and Solaris.}
	\end{itemize}

\end{itemize}

\resheading{Volunteer Experience}
\begin{itemize}
\item
        \ressubheading{Midland Park Ambulance Corps}{Midland Park, NJ}{}{January 2006 - Present}
        \begin{itemize}
                \resitem{Sole person responsible for engineering and administration of
                  mission-critical internal network, applications and
                  Internet-accessible resources supporting 911 Emergency
                  Medical response as a local, county and state resource.}
                \resitem{Responsible for design, development and ongoing support (production
                  status since January 2006) of a custom application to
                  collect and store patient care records (currently in second version).}
                \resitem{Responsible for development, support and ongoing
                  improvements to PHP EMS Tools, a web-based application for
                  scheduling, roster and certification tracking and day-to-day
                administrative tasks for volunteer emergency services
                organizations. In production at Midland Park Ambulance Corps
                since January 2007. (See below, ``Projects''.)}
%                \resitem{Responsible for programming, maintenance and upkeep
%                  of all radio communications equipment.}
                \resitem{Served in numerous capacities including Crew Chief,
                  By-Laws Committee Chairman, Computer Committee Chairman,
                  Treasurer and First Lieutenant (second-in-command).}
                \resitem{Developed VoIP-based system for EMTs to notify
                  dispatch of their response to an emergency call.}
        \end{itemize}
\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
Extensive experience with PHP, Python, Bash/Sh, SQL. Moderate skill in Perl, Java. Basic knowledge of C.
\item[Operating Systems:]
Nine years experience in use and administration of Linux. 5+ years experience administering production/critical Linux servers.
Majority of recent experience with CentOS/RedHat 5 and 6; former experience with SuSE
(7.3-11.3). Basic Solaris 9/10 skills (mainly migration to Linux). Vyatta Network OS, Cisco CatOS and IOS. MacOS (user).
\item[Software:]
Strong: Puppet/Foreman, ISC dhcpd, FreeRADIUS, rsyslog, Nagios/Icinga, Cacti, Bacula, Apache HTTPD, MySQL, Postfix, Procmail, MediaWiki, IPtables, Vyatta router/firewall. Moderate: ISC BIND9, Asterisk, Subversion (SVN), WordPress, OCS Inventory, OpenLDAP, Veeam One, rsync. Basic: NIS (ypserv), Dovecot, CUPS, Xen and VMWare virtualization (vCenter/vSphere), Tomcat, RoR/Phusion Passenger, Redmine, Apache SOLR, Vignette7/8, Resin, memcached, Tidal Enterprise Scheduler. Strongest Network Protocols: RADIUS, DHCP, DNS, SNMP.

%\item[Network Protocols:]
%HTTP(S), LDAP, RADIUS, DHCP, SSH, DNS, IMAP(S), SMTP(S), SNMP, NFS, TFTP, IAX2.

\item[Hardware:]
HP Proliant, Sun, Dell and SuperMicro x86/x86-64 servers, HP iLO, Sun iLOM. Linux- and
BSD-based network devices. Soekris embedded computers, Meru and BlueSocket
wireless access points and controllers. Cisco network hardware. Avocent/Cyclades ACS console servers. F5 BigIp load balancers. Experience with physical infrastructure maintenance (copper, fiber, power) and data center operations.
\end{description}

\resheading{Open Source Projects and Contributions}
\begin{description}
\item{See github.com/jantman}
\end{description}
%%%%%%%%%%%%%%%%%%%%%%
%\resheading{References}
%\begin{description}
%\item{Available upon request.}
%\end{description}

\end{document}
