% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd or http://www.gratisoft.us/todd/resume.html
% (c) 2009 Jason Antman <jason@jasonantman.com> http://www.jasonantman.com
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Jason Antman}  & 201.906.7347 (phone)\\
32 Oak Hill Road &  jason@jasonantman.com \\
Midland Park, NJ 07432& http://resume.jasonantman.com\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Rutgers University}{Piscataway, NJ}{Major in Information Technology and Informatics}{January 2006 - Present}
	\begin{itemize}
		\resitem{Expected to complete all course work by July 2009 for
                  October 2009 graduation.}
                \resitem{Currently 96 credits earned, 113 credits at end of
                  Spring 2009.}
                \resitem{Minor in General History.}
	\end{itemize}
\item
	\ressubheading{Rochester Institute of Technology}{Rochester, NY}{Fine Art Photography Major}{September - December 2005}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Rutgers University - Central Systems \& Services}{Piscataway, NJ}{Student Systems Programmer}{September 2007 - Present}
	\begin{itemize}
                \resitem{Directly assisted Telecommunications Analyst with
                  installation of over 400 wireless access
                  points as well as related planning and support.}
                \resitem{Assisted wireless project manager in troubleshooting
                  and support of University-wide wireless network.}
                \resitem{Time-critical support and troubleshooting of wired
                  connectivity to ``smart'' classrooms across five campuses.}
                \resitem{Assisted system administrators responsible for field repair and support of fifteen student computing
                  labs across five campuses.}
                \resitem{As-needed systems support and development including
                  installation, configuration and troubleshooting of 
                  Linux-based servers and embedded systems.}
                \resitem{Responsible for troubleshooting and operating system
                  configuration/modification of Linux-based embedded systems.}
	\end{itemize}

\item
        \ressubheading{Sun Microsystems}{Somerset, NJ}{Campus Ambassador}{September 2007 - June 2008}
        \begin{itemize}
                \resitem{Campus Ambassador to Rutgers University, responsible
                  for spreading awareness of Sun's open-source product
                  offerings among students, faculty, and staff.}
                \resitem{Sun trained in Solaris 9/10/11,
                  NetBeans, J2SE, J2ME and J2EE. }
                \resitem{Direct contact with Sun engineers for hardware as
                  well as Java and Solaris projects.}
        \end{itemize}

\item
        \ressubheading{Freelance System Administration/Programming}{ }{ }{September 2007 - Present}
        \begin{itemize}
               \resitem{Various freelance system administration and
                 programming projects.}
               \resitem{Developed and implemented PHP-based invoice printing
                 system for electrical parts distributor.}
               \resitem{Performed full backup, analysis, recovery and documentation of a
                 custom system broken and abandoned by previous consultant.}
               \resitem{Migrated corporate accounts receivable/payable access
                 from legacy Telnet-based system to secure SSH-based system.}
               \resitem{Backed up and recovered long-neglected SCO Unix server
                 for a national shipping company.}
               \resitem{Developed and implemented Intranet-based shipment tracking and
                 inventory control system for an ISO 9001-certified courier
                 and freight carrier.}
        \end{itemize}

\item
        \ressubheading{Pulse Medical Transportation}{West Paterson, NJ}{EMT}{May - August 2007}
        \begin{itemize}
                \resitem{Responsible for care of patients on Basic Life
                  Support (BLS) ambulances, as well as working as part of a
                  Neonatal Intensive Care Unit (NICU) or Critical Care Unit
                  (CCU) team on Specialty Care
                  ambulances during inter-facility critical care transports
                  (40-60 hours/week).}
        \end{itemize}

\item
	\ressubheading{Rutgers University - NetOps}{Piscataway, NJ}{Student Systems Programmer}{April 2006 - May 2007}
	\begin{itemize}
		\resitem{Responsible for various web application programming projects, primarily developed for
                  PHP/MySQL on Linux and Solaris.}
	\end{itemize}

\item
        \ressubheading{RIT SportsZone}{Rochester, NY}{Video Editor}{September - November 2005}
        \begin{itemize}
                \resitem{RIT SportsZone is ESPN’s original pilot program for a
                bi-weekly collegiate sports network. The station operates
                within Rochester Institute of Technology, and is entirely
                student-run. My role was an on-call video editor, working in a
                fast-paced production environment with strict deadlines which
                often required working weekends, odd hours, and short stints
                between classes. All editing was performed on Final Cut Pro
                workstations. }
        \end{itemize}

\item
        \ressubheading{DWJ Television}{Ridgewood, NJ}{Assistant Editor}{June 2002 - February 2003}
        \begin{itemize}
                \resitem{Responsible for day-to-day technical operations and
                  first-level support of fast-paced video post-production
                  company.}
                \resitem{After September 2002, lead technician in
                  absence of video engineer. Responsible for operation,
                  troubleshooting and repair of various Sony and Panasonic video equipment,
                  tape decks (DVCAM, DVCPRO, Beta, VHS, 3/4'' and 1''), BTS
                  Venus switcher, satellite and fiber uplinks, and duplication
                  equipment.}
                \resitem{Video editing on Sony linear and Avid Media Composer
                  non-linear editing systems.}
                \resitem{Supported four Apple PowerPC/Avid editing suites.}
                \resitem{Responsible for recording and post-production of
                  soundtracks and voiceovers in absence of audio engineer.}
                \resitem{Sole person responsible for maintenance and upkeep of corporate
                  60,000+ item mixed-media tape archive.}
                \resitem{Acted as technician/assistant director for live
                  news events uplinked nationally via satellite.}
        \end{itemize}

%\pagebreak 
\end{itemize}

\resheading{Volunteer Experience}
\begin{itemize}
\item
        \ressubheading{Midland Park Ambulance Corps}{Midland Park, NJ}{ }{December 2005 - Present}
        \begin{itemize}
                \resitem{Computer Committee member since 2006, Chairman since
                  January 2008.}
                \resitem{Chairman, By-Laws Committee since 2008.}
                \resitem{Responsible since 2006 for administration and engineering of
                  mission-critical internal network, applications and
                  Internet-accessible resources supporting 911 Emergency
                  Medical response as a local, county and state resource.}
                \resitem{Responsible for single-handed development (production
                  status since January 2006) and ongoing support of a custom
                  HIPPA-compliant application to collect and store patient
                  care records.}
                \resitem{Responsible for development, support and ongoing
                  improvements to PHP EMS Tools, a web-based application for
                  scheduling, roster and certification tracking and day-to-day
                administrative tasks for volunteer emergency services
                organizations. In production at Midland Park Ambulance Corps
                since January 2007. Currently licensed under GNU GPL with over
                800 downloads from SourceForge.}
                \resitem{Developed ieilogd, a Unix daemon to log evens from
                  IEI physical access control systems and correlate logs with
                  a membership/users database. Production status since March
                  2008 and released under GNU GPL.}
                \resitem{Responsible for programming, maintenance and upkeep
                  of all radio communications equipment}.
                \resitem{NJ State Certified EMT, certified in Incident Command
                System (ICS), PHTLS, CPR, NIMS.}
                \resitem{Served as EMT and crew chief for numerous major
                  incidents.}
        \end{itemize}

\item
        \ressubheading{Boro Of Midland Park}{Midland Park, NJ}{}{November 2008 - Present}
        \begin{itemize}
                \resitem{Volunteer IT consultant to the Midland Park Town
                  Council on an as-needed basis.}
                \resitem{Provide an IT-oriented viewpoint to the Town Council on
                  policy, implementation and contract issues for town website,
                  Internet-based town-wide communication systems and other IT matters.}
        \end{itemize}
\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
PHP, Python, Bash/Sh, SQL. Basic (student's) knowledge of Java, Perl, C, Assembly,
PCL. 
\item[Operating Systems:]
Use and administration of Linux (various distributions) since 2001 (8
years). 4 years experience in administering production Linux servers, 3 years
administering mission-critical public safety servers. Experience in embedded
Linux development. 
Sun-trained in Solaris 9/10/11. Mac OSX (desktop). 
\item[Software:]
Apache HTTPD, MySQL, Postfix, SpamAssassin, Procmail, Dovecot, Cyrus SASL, BIND9 (ISC), ISC
DHCPD, Nagios. Munin, Cacti/RRDtool, OpenLDAP, OpenSSH, Bacula,
OpenSSL, CUPS, Syslog-ng, CVS, Subversion, MediaWiki, Eventum. IPtables
(firewall) and Vyatta firewall/router platform. Xen
virtualization. VoIP / Asterisk.
\item[Hardware:]
Soekris embedded computers, Meru and BlueSocket wireless access points. Linux-
and BSD-based network devices. Dell,
HP Proliant and Sun servers. Cisco network hardware. Linksys, 3COM, HP
ProCurve switches. DOCSIS-compliant cable
modems. Avocent console servers. Apex and
Avocent KVM switches.
\end{description}

\resheading{Projects}

\begin{description}
\item[In Progress] RackMan, a web-based tool to track locations of hardware
  within server racks, automatically discover and track connections between
  devices, and allow simulations of various equipment placement schemes.
\item[2007--Present] PHP EMS Tools (www.php-ems-tools.com) - a scheduling and
  administrative tool for emergency services agencies, coded in PHP with a MySQL
  backend. GPL-licensed Free/Open Source with over 800 downloads.
\item Various smaller projects including PHP-based SNMP printer management and
PHP/CUPS print accounting with a web-based interface.
\item TuxTruck, a Linux-based in-vehicle computer including navigation,
  multimedia, and communications capabilities. Implemented in software only
  due to high prototype cost.
\item TuxoStat, a proof-of-concept Linux-based home thermostat with full
  heating/cooling control, multi-zone temperature sensors and infinitely
  fine-grained scheduling.
\end{description}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Activities}
	\begin{description}
		\item Member, USENIX SAGE (System Administration special
                  interest group).
                \item Member, League of Professional System Administrators
                  (LOPSA), New Jersey chapter.
                \item Volunteer Emergency Medical Technician (see above).
                \item Rutgers University Student Linux Users' Group
                  (RUSLUG). Member 2006-2009, President 2008-2009.
                \item 2005 recipient of the Raoul Wallenberg Humanitarian
                  Award (for high school students) presented by the Greater
                  New York Wallenberg Committee, for activities supporting
                  local homeless outreach program.
	\end{description}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{References}
\begin{description}
\item{Available upon request.}
\end{description}

\end{document}
